\bf Supervised tensor decomposition with features on multiple modes

### 2021-06-21 tensor_regress/JCGS/Revision/manuscript/response.tex

Figure~\ref{fig:noniid}a-b assesses the impact of noise correlation to the estimation accuracy. The data is simulated from {\bf Envelope} model with envelope dimensions $r=(3,3)$ (low) and $(4,5)$ (high). The noise is generated from a zero-mean Gaussian tensor with Kronecker structured covariance; see Supplementary Notes for details. As expected, {\bf Envelope} shows the best performance in the high correlation setting. Remarkably, we find that our method {\bf STD} has comparable and sometimes better performance when noise correlation is moderate-to-low. In contrast, {\bf SupCP} appears less suitable in this setting. Although {\bf SupCP} allows noise correlation implicitly through latent random factors, the induced correlation may not belong to the Kronecker covariance structure in the simulation.

Figure~\ref{fig:noniid}c-d assesses the impact of sparsity to estimation performance. We generate data from {\bf GLSNet} model, except that we modify the coefficient tensor to be joint sparse and low-rank (the original {\bf GLSNet} model assumes full-rankness on the coefficient tensor). 
The sparsity level ($x$-axis in Figure~\ref{fig:noniid}c-d) quantifies the proportion of zero entries in the coefficient tensor. Since neither our method {\bf STD} nor {\bf GLSNet} follow the simulated model, this setting allows a fair comparison. We find that our method outperforms {\bf GLSNet} in the low-rank setting, whereas {\bf GLSNet} shows a better performance in the high-rank setting. This observation suggests the robustness of our method to sparsity when the tensor of interest is simultaneously low-rank and sparse. When sparsity is the only salient structure, then methods specifically addressing sparsity would provide a better fit.''

\begin{figure}[htb]
\centering
\includegraphics[width=12cm]{noniid_final.pdf} 
\caption{Comparison between tensor methods under model misspecification. Panels (a)-(b) assess the error correlation, and panels (c)-(d) assess the sparsity. }~\label{fig:noniid}
 \end{figure}

 \end{quote}

 For self-consistency, we quote the detailed simulation setups for the Figure~\ref{fig:noniid} in the Supplementary Notes, Section \ref{sec:asimulation}:
\begin{quote}
    ``
    \textbf{B.1 Detailed simulation setup for Figure~\ref{fig:noniid}a-b}

    \vspace{0.2cm}

    We generate data from \textbf{Envelope} model \citep{li2017parsimonious} with slight modification. We simulate response tensor $\tY\in\mathbb{R}^{d\times d\times d}$ from the following model with envelope dimension $(u_1, u_2)$,
\begin{align}\label{eq:e}
    \tY|\mX &= \tB \times_3 \mX + \tE = \tC \times \{\mGamma_1, \mGamma_2,\mX\}+ \tE, \notag \\
    \text{with} \quad \tE &\sim \mathcal{TN}(\mSigma_1, \mSigma_2, \mI), \quad \mSigma_k = \mGamma_k \mOmega_k \mGamma_k^T + \mGamma_{0k} \mOmega_{0k} \mGamma_{0k}^T+\mI, \quad k = 1,2,
\end{align}
 where $\mX\in\mathbb{R}^{d\times p}$ is the feature matrix, $\tB=\tC\times\{\mGamma_1,\mGamma_2, \mI\}\in \mathbb{R}^{d\times d\times p}$ is the coefficient tensor, $\tC\in\mathbb{R}^{\mu_1\times \mu_2\times p}$ is a full-rank core tensor, $\mathcal{TN}(\cdot,\ \cdot,\ \cdot)$ represents zero-mean tensor normal distribution with Kronecker structured covariance, 
 $\mGamma_{k} \in \mathbb{O}(d,u_k)$ 
 consists of orthogonal columns, $\mGamma_{0k} \in \mathbb{O}(d,d-u_k)$ is the orthogonal complement of $\mGamma_k$, and  $\mOmega_k = \mA_k\mA_k^T$, $\mOmega_{0k} = \mA_{k0}\mA_{k0}^T$ with $\mA_k \in \bbR^{u_k \times u_k}$,  $\mA_{k0} \in \bbR^{(d - u_k) \times (d - u_k)}$.

 The entries of $\mX$ are i.i.d.\ drawn from $\tN(0,1)$, the entries of $\mA_k$, $\mA_{k0}$ are i.i.d.\ drawn from $\textup{Uniform}[-\gamma, \gamma]$, and the entries of core tensor $\tC$ are i.i.d.\ drawn from $\textup{Uniform}[-3,  3]$. We call $\gamma$ the \textit{correlation level}. Note that the only distinction between model~\eqref{eq:e} and standard {\bf Envelope} model is the additional identity matrix $\mI$ in the expression of $\mSigma_k$. When $\gamma = 0$, the model~\eqref{eq:e} reduces to our \textbf{STD} model with rank $\mr = (u_1,u_2,p)$. We set $d=20, p=5$ in our simulation.

 \vspace{0.2cm}
 \textbf{B.2 Detailed simulation setup for Figure~\ref{fig:noniid}c-d}

 \vspace{0.2cm}

We generate the data from  \textbf{GLSNet} model \citep{zhang2018network} with slight modification. We simulate the binary response tensor $\tY \in \{0,1\}^{d \times d \times d}$ from the following model
\begin{align}
    \mathbb{E}[\tY|\mX] = f({\bf 1} \otimes {\bf \Theta} + \tB \times_3 \mX),
\end{align}
where $f(\cdot)$ is the logistic link, $\mX \in \mathbb{O}(d,p)$ is the feature matrix with orthonormal columns, ${\bf \Theta}=\mA \mA^T \in \bbR^{ d \times d }$ is a rank-$R$  intercept matrix, where the entries of $\mA \in \bbR^{d \times R}$ are simulated from i.i.d.\ standard normal. 
Unlike original \textbf{GLSNet} model, we generate joint sparse and low-rank structure to the coefficient tensor $\tB$ as follows.

To generate $\tB$, we firstly generate a low-rank tensor $\tB_0$ as 
\begin{align}
    \tB_0 = \tC \times \mM_1 \times \mM_2 \times \mM_3,
\end{align}
where $\tC \in \bbR^{R \times R \times R}$ is a full-rank core tensor, $\mM_1, \mM_2 \in \bbR^{d \times R}$ and $\mM_3 \in \bbR^{p \times R}$ are the factor matrices with orthonormal columns. We simulate i.i.d.\ uniform entries in $\tC$ and rescale the tensor $\tB_0$ such that $\onorm{\tB_0}_{\max} = 2$. Last, we obtain a sparse $\tB$ by randomly setting $sd^2p$ entries in $\tB_0$ to zero. We call $s$ the \textit{sparsity level} which quantifies the proportion of zero's in $\tB$. Hence, the generated tensor $\tB$ is of sparsity level $s$ and of low-rank $(R,R,R)$. We set $d = 20$, $p = 5$ and consider the combination of rank $R = 2$ (low), $4$ (high) and sparsity level $s = \{0, 0.3,0.5\}$ in the simulation. "

\end{quote}

\end{enumerate}

    \item \textit{Additional discussion on side information should be included that involves i) how do we know in practice if side information is appropriate; ii) dimensionality of the side information.}

    \vspace{0.2cm}
    \textbf{Response:} See our response to \textbf{\# 5, Reviewer 2}.

    \item \textit{The authors should discuss initialization and how to obtain the initial error condition. Can something be said about the proposed random initialization in Algorithm 1?}

         \textbf{Response:} We have added theoretical justifications to two initializations. See our response {\bf \# Initialization, Reviewer 1.}

    \item \textit{There is a disconnect between the proposed algorithm and established theory. Can the authors establish statistical properties for the iterative algorithm? If not, what are the technical challenges that are not present in the related literature?}

     \textbf{Response:} We have added new theory to establish the accuracy for both (i) global MLE and (ii) local optimizer. See our response to {\bf \# Theoretical Studies, Reviewer 1.}

    \item \textit{Some discussion on the computationally tractable selection of ranks should be included. See comment from Reviewer 2.}

    \textbf{Response:} We have added more detailed discussions and reported the running time for rank selection. See our response to \textbf{\# 8, Reviewer 2}.
\end{enumerate}

\newpage

\begin{center}
    \textbf{Point-by-point Response to Reviewer 1}
\end{center}

We greatly appreciate your valuable comments and suggestions. We have carefully addressed all the questions. Note that general comments raised by both reviewers were addressed upfront in {\bf pages 1-7 of this response letter, Response to Major Comments Summarized by Editor}. We will make explicit reference to earlier section when needed.

\vspace{0.2cm}

\textit{This paper introduces a novel supervised tensor decomposition model when there are side information on multiple modes. This model can be viewed as an extension to tensor response regression. As compared to existing tensor response regression models \citep{rabusseau2016low,li2017parsimonious,sun2017store}, the proposed method has three advantages. First, it allows covariate information on multiple modes instead of one mode. Second, it allows high-dimensionality on both the tensor size $d_k$ and covariate size $p_k$. Third, it allows a ﬂexible data type of the tensor, including continuous, count, and binary observations. Data satisfying these properties are not rare, and the paper has provided three data examples. Therefore, I believe this is a useful and well-motivated work. The construction of the estimator leads to a non-convex optimization. Both algorithm and theoretical study are constructed. This work can be regarded as a non-trivial extension of these tensor response regression models as well as \cite{wang2020learning} on probabilistic tensor decomposition which decomposes a tensor with continuous, count, or binary observations. Overall, I think this is an interesting work that has potential usefulness and will contribute to the literature of tensor regression. I enjoy reading the paper and feel it would be suitable for JCGS if the following comments are addressed. I recommend a major revision.}

\vspace{0.2cm}
\textit{\textbf{Initialization:}}
\begin{enumerate}[wide, labelwidth=!, labelindent=0pt]
    \item \textit{How to initialize to achieve the initial error condition, as stated in Proposition 4.1 (Global convergence)?}

    {\bf Response:} We recommend two schemes for initialization: random initialization (cold start) and spectral initialization (warm start). In the high signal-to-noise regime, we have added theoretical guarantees for the statistical accuracy of warm start within polynomial running time. In the low signal-to-noise regime, the statistical-computational gap arises in which case random initialization often provides better empirical results. {\bf We have added a new section for provable initialization and its implementation.} See our detailed response to  {\bf\# Theoretical Studies}.

    We have added the following paragraph in Section~\ref{sec:rankM}:
    \begin{quote}
    ``...We provide two initialization schemes, one with QR-adjusted spectral initialization (warm initialization), and the other with random initialization (cold initialization). The warm initialization is an extension of unsupervised spectral initialization~\citep{zhang2018tensor} to supervised setting with multiple feature matrices. ... The initialization scheme is described in Algorithm~\ref{alg:A}.

The warm initialization enjoys provable accuracy guarantees at a cost of extra technical assumptions (see Section~\ref{subsec:statprob}). The cold initialization, on the other hand, shows robust in practice but its theoretical guarantee remains an open challenge~\citep{luo2021low}. We incorporate both options in our software package to provide flexibility to practitioners...''
\end{quote}

\begin{algorithm}[!h]
\caption{QR-adjusted spectral initialization}\label{alg:A}
\begin{algorithmic}[1]
\INPUT Response tensor $\tY\in \mathbb{R}^{d_1\times \cdots \times d_K}$, feature matrices $\mX_k\in\mathbb{R}^{d_k\times p_k}$, Tucker rank $\mr$. 
\State Normalize date tensor $\bar \tY\leftarrow \tY$ for Gaussian model, $\bar \tY\leftarrow 2\tY-1$ for Bernoulli model, and $\bar \tY\leftarrow \log(\tY+0.5)$ for Poisson model. 
\State Normalize feature matrices via QR factorization $\mX_k=\mQ_k\mR_k$ for all $k\in[K]$.
\State Obtain $\bar \tB \leftarrow \bar \tY\times\{\mQ^T_1,\ldots,\mQ^T_K\}$ by projecting $\bar \tY$ to the multilinear feature space. 
\State Obtain $\hat\tB^{(0)}\leftarrow \textup{HOSVD}(\bar \tB,\mr)$.
\State Normalize representation $\{\hat\tC^{(0)}, \hat\mM^{(0)}_1,\ldots,\hat\mM^{(0)}_K\}$ such that $\hat\tC^{(0)}\times\{ \hat\mM^{(0)}_1,\ldots,\hat\mM^{(1)}_K\} = \hat\tB^{(0)}\times\{ \mR^{-1}_1,\ldots,\mR^{-1}_K\}$ and $\hat\mM^{(0)}_k\in\mathbb{O}(p,r)$ for all $k\in[K]$.
\OUTPUT Core tensor $\hat\tC^{(0)}$ and factors $\hat\mM^{(0)}_k$ for all $k\in[K]$.
\end{algorithmic}
\end{algorithm}

    \item  \textit{As the proposed estimator is obtained from a nonconvex optimization, the possibility of having multiple local optimizers is a problem. In Algorithm 1, a random initialization is used. Can the authors construct an empirical study of how serious the local optimal affects the statistical performance of the randomly initialized estimator? Does the random initialization always lead to the global optimum?}

     \textbf{Response:} The empirical performance of random initialization was investigated in Figure~\ref{fig:loglike} in the original paper and the remarks thereof. We have shown in Theorem~\ref{thm:MLE} that the same statistical rate holds, not only for the {\it global optimizer}, but also for every {\it local optimizer} with sufficiently large objective values. In this sense, local optimality is not necessarily a severe concern in our context. We have added the following sentences for clarification in Sections~\ref{sec:global} and Section~\ref{sec:local}:

     \begin{quote}
         ``...Inspection of our proof (Supplementary Notes) shows that the desired convergence rate holds not only for the MLE, but also for all local optimizers in the set $\tL_{\tY}(\tC, \mM_1,\ldots,\mM_K)\geq \tL_{\tY} (\tC_{\textup{true}},\mM_{1,\textup{true}},\ldots,\mM_{K,\textup{true}})$. The observation indicates the global optimality is not necessarily a serious concern in our context, as long as the convergent objective is large enough. In next section, we will provide the statistical accuracy for \emph{local} optimizer with provable convergence guarantee, at a cost of extra signal requirement...''
     \end{quote}

     \begin{quote}
     ``...We supply the theory by providing an alternative scheme -- random initialization -- and investigate its empirical performance. Figure~\ref{fig:loglike} shows the trajectories of objective function ... In the experiment we conduct, we find random initialization appears good enough for Algorithm~\ref{alg:B} to find a convergent point with desired statistical guarantees. In practice, we recommend to run both warm and cold initializations, and choose the one with better convergent objective values...''
     \end{quote}

     On a related note, characterizing the optimization landscape and impact of initialization are problems of interest. Inspired by the reviewer's comment, {\bf we have added new theory for provable initialization and per-iteration accuracy.} See our response to {\bf\# Theoretical Studies}.

     \begin{quote}

\end{quote}

\end{enumerate}

\vspace{0.2cm}
\textit{\textbf{Theoretical Studies:}}

\begin{enumerate}[wide, labelwidth=!, labelindent=0pt]
    \item \textit{The statistical properties established in Theorem 4.1 is for the M-estimator in (8). However, due to non-convexity of this optimization, the maximizer of (8) may not be achievable by practical algorithms. Therefore, it would be more convincing to prove statistical properties for the iterative estimator from the alternating optimization in Algorithm 1. Such theorem is pretty standard in recent tensor regression models with low-rank structure \citep{sun2017store, raskutti2019convex,hao2019sparse,han2020optimal}. If this proof is not possible, it would be helpful if the authors could discuss the technical challenges.}

    {\bf Response: }Thank you for the suggestion. Inspired by your comments, we have now proved the statistical properties for the iterative estimator from the alternating optimization in Algorithm 1. We summarize the new results below; the detailed revisions are in Section~\ref{subsec:statprob}.

     \begin{quote}
    ``...This section presents the accuracy guarantees for both global and local optimizers of~\eqref{eq:MLE}. We first provide the statistical accuracy for the global MLE~\eqref{eq:MLE}. Then, we provide the convergence rate for the local optimizer from Algorithm~\ref{alg:B} with warm initialization. The rate reveals an interesting interplay between statistical and computational efficiency. We show that a polynomial number of iterations suffices to reach the desired accuracy under certain assumptions...'' 
    \end{quote}

     \begin{quote}
``...Under mild conditions, our warm initialization enjoys stable performance, and the subsequent iterations further improve the accuracy via linear convergence; i.e.\ sequence of iterates generated by Algorithm~\ref{alg:B} converges to optimal solutions at a linear rate.

\begin{prop}[Polynomial-time angle estimation]\label{lem:ini} Consider Gaussian tensor models with $b(\theta)=\theta^2/2$ in the objective function~\eqref{eq:loglikelihood}. Suppose the signal-to-noise ratio $\lambda^2/\phi \geq C p^{K/2}d^{-K}$ for some sufficiently large universal constant $C>0$. 
Under Assumption A1 with scaled feature matrices $\bar \mX_k=\sqrt{d}\mX_k$, or Assumption A1' with original feature matrices, the outputs from initialization Algorithm~\ref{alg:A} and iteration Algorithm~\ref{alg:B} satisfy the following two properties.
\begin{enumerate}[label=(\alph*)]
\item With probability at least $1-\exp(-p)$. 
\begin{equation}\label{eq:warm}
\max_{k\in[K]}\sin^2\Theta(\trueM,\hat \mM_k^{(0)})\leq {1\over 4}. 
\end{equation}
\item Let $t=1,2,3,\ldots,$ denote the iteration. There exists a contraction parameter $\rho\in(0,1)$, such that, with probability at least $1-\exp(-p)$, 
\begin{equation}\label{eq:local}
\max_{k\in[K]}\textup{sin}^2 \Theta(\trueM, \hat \mM^{(t)}_k) \lesssim \KeepStyleUnderBrace{{\phi p \over \lambda^2 d^K}}_{\text{statistical error}}+\KeepStyleUnderBrace{\rho^{t}\max_{k\in[K]}\textup{sin} \Theta^2(\trueM, \hat \mM_k^{(0)})}_{\text{algorithmic error}}.
\end{equation}
\end{enumerate}
\end{prop}

### 2021-06-21 tensor_regress/JCGS/Revision/manuscript/response.tex

Proposition~\ref{lem:ini} provides the estimation errors for algorithm outputs at initialization and at each of the subsequent iterations. The initialization bound~\eqref{eq:warm} demonstrates the stability of QR-adjusted spectral initialization under a mild SNR requirement $\lambda^2/\phi \gtrsim p^{K/2}d^{-K}$. We can think of $d$ as the sample size while $p$ the number of parameters at mode $K$. The condition confirms that a higher sample size mitigates the required signal level. The iteration bound~\eqref{eq:local} consists of two terms: the first term is the statistical error, and the second is the algorithmic error. The algorithmic error decays exponentially with the number of iterations, whereas the statistical error remains the same as $t$ grows. The statistical error is unavoidable and also appears in the global MLE; see Theorem~\ref{thm:MLE}.

As a direct consequence, we find the optimal iteration $t$ after which the algorithmic error is negligible compared to statistical error. 
\begin{thm}[Statistical rate for local optimizers]\label{thm:local}Consider the same condition as in Proposition~\ref{lem:ini} and the outputs by combining algorithms 1 and 2. There exists a constant $C>0$, such that, after $t\gtrsim K\log_{1/\rho}p$ iterations, our algorithm outputs satisfies
\[
\max_{k\in[K]}\textup{sin}^2 \Theta(\trueM, \hat \mM^{(t)}_k) \lesssim {\phi p\over \lambda^2d^K}, \quad \FnormSize{}{\trueB- \hat \tB^{(t)}}^2 \lesssim {\phi(r^K+Kpr)\over d^K}.
\]
\end{thm}

In practice, the signal level $\lambda$ is unknown, so the assumption in Theorem~\ref{thm:local} is challenging to verify in practice. We supply the theory by providing an alternative scheme -- random initialization -- and investigate its empirical performance...''

    \end{quote}

    \item \textit{As shown in Theorem 4.1, the rate of convergence is in the order $\sum_k p_k/ \prod_k d_k$ when other terms fixed. Here $p_k$ is the covariate size along $k$-th mode. I am curious if there is any insight on the optimality of this scaling. Since handling multiple covariates is one of the key contributions of this work, I think more discussion of the order of $p_k$ would be useful. For instance, it would be helpful to compare this rate with the optimal rate established in tensor regression \citep{han2020optimal} and probabilistic tensor decomposition \citep{wang2020learning}. }

    {\bf Response:} We have explained the intuition about our optimality and the benefit of incorporating multiple feature matrices. We added discussions to the scaling factors in Section~\ref{subsec:statprob}:

\begin{quote}
``...The result in~\eqref{eq:bound} implies that the estimation has a convergence rate $\tO(Kp/d^{K})$...This rate agrees with intuition, since in our setting, the number of parameters with $K$ feature matrices is of order $\tO(Kp)$, whereas the number of tensor entries $\tO(d^K)$ corresponds to the total sample size. Because $p\leq d$, our rate is faster than $\tO(d^{-(K-1)})$ obtained by tensor decomposition without features~\citep{wang2020learning}..''

``...The initialization bound~\eqref{eq:warm} demonstrates the stability of warm initialization under a mild SNR requirement $\lambda^2/\phi \gtrsim p^{K/2}d^{-K}$. We can think of $d$ as the sample size while $p$ the number of parameters at mode $K$. This threshold is less stringent than $d^{K/2}$ required for tensor decomposition without multiple features~\citep{han2020optimal,zhang2018tensor}...''
\end{quote}
\end{enumerate}

\vspace{0.2cm}
\textit{\textbf{Numerical comparison:}}
\begin{enumerate}
    \item \textit{In Section 5.2 (simulation) and Section 6.1 (HCP data), only the multiple-response GLM method is compared. This setting seems to be a special case of the network response regression \citep{zhang2018network}, therefore it would be interesting to add it in the comparison. If they are not directly comparable, it would be helpful to discuss it.}

    \textbf{Response:} We have added comparison with 12 methods, including GLSNet~\citep{zhang2018network}, in the new Section~\ref{sec:connection}. For alternative methods in numerical analysis, we have also replaced the earlier old methods by more recent methods, including~\cite{zhang2018network}, in Section~\ref{sec:simulation}. See our response to \textbf{\# 1, Major Comments Summarized by Editor} for full details.

    \item \textit{There are other recent tensor response regression models \citep{li2017parsimonious,sun2017store,raskutti2019convex}. Some of them are missing in the paper. It would be interesting to see the comparison with more recent tensor response regression models in Section 5.3. If they are not directly comparable, it would be helpful to discuss it.}

    \textbf{Response:} We have made changes as suggested. Comparisons are summarized in our response to \textbf{\# 1, Major Comments Summarized by Editor}. 
\end{enumerate}

\vspace{0.2cm}
\textit{\textbf{Minor issues and typos:}}

\begin{enumerate}
     \item \textit{The notation $\alpha$ is used for both the maximum norm constraint on page 13, and the signal level on page 19. Are they same? If not, it would be helpful to use different notations.}

         \textbf{Response:} 
        They are the same. The sentence now reads:
         \begin{quote}
             ``... Here $\alpha>0$ controls the magnitude of the effect size, which is also the maximum norm of coefficient tensor as in~\eqref{eq:p}...."
         \end{quote}

    \item \textit{In the optimization (8), the authors add a maximum norm constraint on the linear predictor to avoid the divergence in the non-Gaussian variance. Can authors provide more explanations on this constraint? }

    \textbf{Response:} We have added the following explanation in Section~\ref{sec:rankM}:
    \begin{quote}
       ``...The maximum norm constraint on the linear predictor $\Theta$ is a technical condition to ensures the existence (boundedness) of MLE. 
The condition precludes the ill-defined MLE when the optimizer of~\eqref{eq:MLE} diverges to $\pm \infty$; this phenomenon may happen in logistic regression when the Bernoulli responses $\{0,1\}$ are perfectly separable by covariates~\citep{wang2020learning}. For Gaussian models, no maximum norm constraint is needed. In Section~\ref{subsec:statprob}, we show that setting $\alpha$ to an extremely large constant does not compromise the statistical rate in quantities of interest. In practice, the unbounded search is often indistinguishable from the bounded search, since the boundary constraint $\onorm{\Theta}_{\infty} \leq \alpha$ would likely never be active. Similar techniques are commonly used in high-dimensional non-Gaussian problems~\citep{wang2020learning,han2020optimal}...''
    \end{quote}

     \item \textit{What’s the tuning range for the ranks $r_1,...,r_K$ in the experiments?}

     \textbf{Response:} 
     For simulation, we have added the following details in Section~\ref{sec:simulation}:
     \begin{quote}
         ``...For each combination, we minimize BIC using a grid search from $(r_1-3, r_2-3, r_3-3)$ to $(r_1+3, r_2+3, r_3+3)$. We remove invalid rank combinations such as $r^2_{\max} \geq \prod_{k=1}^3 r_k$ and use parallel search to reduce the computational cost....'' 
     \end{quote}

 For data application, we have added the following clarification in Section~\ref{sec:data}. Detailed rank selection is provided in a new section {\bf Rank selection for Nations data, Supplementary Notes}. 
   \begin{quote}
   ``... We use BIC as guidance to select the rank of coefficient tensor $\tB$. Since several rank configurations give similar BIC values, we present here the most interpretable results with $\mr=(4,4,4)$. Detailed rank selection procedure is in Supplementary Notes...''
\end{quote}

\item \textit{Typos: 1) line -3 on page 18, $\mM_2 \mX_3$ should be $\mM_2\mX_2$; 2) Table 2, the column names $d = 20$ and $d = 40$ are missing.}

\textbf{Response:} We have made the correction as suggested.

\end{enumerate}

\clearpage
\newpage

\begin{center}
    \textbf{Point-by-point Response to Reviewer 2}
\end{center}

We greatly appreciate your valuable comments and suggestions. We have carefully addressed all the questions. Note that general comments raised by both reviewers were addressed upfront in {\bf pages 1-7 of this response letter, Response to Major Comments Summarized by Editor}. We will make explicit reference to earlier section when needed.

{\it The paper develops a Tucker decomposition technique for tensor data, which can consider side information in each mode. In particular, the model is built upon the exponential family to handle non-Gaussian data, and the method is formulated as a generalized tensor regression problem. An alternating algorithm is proposed to estimate the model parameters. The statistical convergence is derived for the proposed method. The applications to a brain imaging example and an international relation example reveal some interesting structures in data. Overall, the paper is well written and easy to read. The numerical results demonstrate the potential utilities of the proposed method. There are a few places where the paper can be further improved. }

\begin{enumerate}[wide, labelwidth=!, labelindent=0pt]
    \item \textit{The term “interactive” is used in the title and throughout the paper. However, it is not very clear from the paper what it means to be interactive. It seems the side information is always assumed given and static. In that case, I would recommend removing the term. }

    \textbf{Response:} We have removed the term as suggested.

    \item \textit{There are quite a few non-Gaussian tensor models for various analyses in the literature \citep{tarzanagh2019regularized, li2020generalized, chi2012tensors, hong2020generalized}. A more thorough literature review is warranted. }

    \textbf{Response:} Thank you for pointing out the related literature. The methods \citep{chi2012tensors, hong2020generalized} were reviewed and compared in the first version. We have added detailed literature discussions with 12 more methods and the numerical comparisons. See our response to \textbf{\# 1, Major Comments Summarized by Editor} for the full comparison.

    \item \textit{The proposed method is closely related to the envelope model (especially for Gaussian data)\citep{li2017parsimonious}. It would be of interest to discuss the similarity and difference between the two.}

    \textbf{Response:} Per reviewer's suggestion, we have added more literature reviews and updated the numerical comparisons. See our response to, \textbf{\# 1, Major Comments Summarized by Editor}.

    \item \textit{The dimension requirements seem unnecessarily strong. In particular, the number of features in the side information ($p_k$) is required to be smaller than the dimension of the corresponding mode of the tensor data ($d_k$); the rank of the core tensor ($r_k$) needs to be smaller than $p_k$. In practice, how to handle a large number of features (i.e., $p > d$)? If the number of features is small (e.g., in the HCP example, there are only 2 individual features where age is further discretized as dummy variables), can the rank of the core tensor exceed the feature dimension? More discussions are needed.}

    \textbf{Response:} There are two questions here, one on $r\leq p$, and the other on $p\leq d$. We discuss them separately.

  {\bf Regarding the condition $r\leq p$.} This is not a requirement but rather a natural fact based on definition of tensor rank.  Notice that $p$ is the dimension of parameter tensor of interest, and $r$ is the rank of the parameter tensor. Numerically, one must have $r\leq p$; i.e, the rank of core tensor cannot exceed the feature dimension.

 From the modeling perspective, the fact $r\leq p$ comes from the goal of the problem: we aim to identify tensor factors that are most attributable to features. In the HCP example, our goal is to find the relationship between data tensor  $\tY\in\{0,1\}^{68\times 68\times 136}$ and the feature $\mX\in\mathbb{R}^{4\times 136}$. The fullest linear model has coefficient $\tB\in\mathbb{R}^{68\times 68\times 4}$, with rank upper bounded by 4 on the last mode.

{\bf Regarding the condition $p\leq d$.} This condition requires the feature to have full column rank. We view it as a mild condition, because same condition is also imposed in classical linear regression. In the presence of rank deficiency, we recommend to remove redundant features before applying our method.

We have added more discussions in Sections~\ref{sec:model} and~\ref{subsec:statprob}. 
\begin{quote}
        ``..the identifiability of $\tB$ requires the feature matrices $\mX_k$ are of full column rank with $p_k\leq d_k$. We impose this rank non-deficiency assumption to $\mX_k$; this is a mild condition common in literature~\citep{lock2018supervised, li2017parsimonious, li2020generalized}. In the presence of rank deficiency, we recommend to remove redundant features from $\mX_k$ before applying our method. ..."
\end{quote}
  \begin{quote}
  ``...the requirement $p\leq d$ is necessary to ensure rank non-deficiency of  feature matrices $\mX_k$..''
  \end{quote}

\item \textit{A related question to the above comment: if the side information is little (small $p_k$) or irrelevant to the underlying structure of the tensor data, would the proposed model structure (3) be overly restrictive rather than helpful? In other words, the “supervised tensor factor” $\mX_k\mM_k$ must reside in the column space of the features $\mX_k$. If $\mX_k$ is not well selected, would that lead to a biased decomposition of the original data? In practice, how do we know if a set of features are appropriate to use? The envelope model \citep{li2017parsimonious,lock2018supervised} may offer an alternative perspective by separating the data variation into a material part (related to $\mX_k$) and an immaterial part (irrelevant to $\mX_k$). It’s not clear whether the idea directly applies to the proposed method in this paper since the low-rank model is on the deterministic mean tensor. Some discussions would be helpful.}

    \textbf{Response:} We agree with the basic premise of the reviewer that the our method relies on the choice of feature matrices. In fact, this does not undermine our method's utility. A major point we want to make in response is that the goal of our problem is to estimate the {\it conditional pattern} of $\tY|\mX$, not the {\it overall pattern} of $\tY$. This motivation has guaranteed the validness (unbiasedness) of our factors, even when the $\mX$ is poorly related to $\tY$. The tensor factors we learned are not intended to explain the most variation in the $\tY$; instead, they are intended to capture the variation that is most attributable to features.

    There are methods that jointly impose data variation in conditional component $\tY|\mX$ and residual component $\tY-\tY|\mX$. These methods have the benefits of joint learning the conditional variation of $\mathbb{E}(\tY|\mX)$ and the variation of residuals. The referred methods, Envelope~\citep{li2017parsimonious} and SupCP~\citep{lock2018supervised}, fall into this category. We have added connection and comparison with these two methods in  Section~\ref{sec:connection} and in Section~\ref{sec:simulation}. See our response to {\bf \# 1, Major Comments Summarized by Editor}.

For reviewer's interest, we discuss the practical guidance about ``which method should we use.'' 
\begin{enumerate}
    \item In general, the answer depends on the goal and problem at hand. If the goal is to identify the relationship between tensor data $\tY$ and features $\mX$, then we would recommend our method. In the three examples  illustrated in Section~\ref{sec:motivation} and two data applications in Section~\ref{sec:data}, we are interested in identifying the relationship between data tensor ( brain connectivities, social community patterns) and available features (age, gender). In these cases, direct modeling $\tY|\mX$ yields a higher accuracy, especially when variation in $\tY|\mX$ is weak compared to the overall variation in $\tY$.

    \item If the goal is to identify unknown variation in the data tensor $\tY$, then we recommend Envelope~\citep{li2017parsimonious} and SupCP~\citep{lock2018supervised}. These two methods have the benefits of separating the variations of $\tY$ into explained part by $\mX$ and unexplained part due to unmeasured latent factors.

    \item If the goal is to identify the relationship between $\tY$ and $\mX$ while adjusting for latent factors, then we would recommend generalized mixed-effect tensor decomposition (MSTD). The MSTD combines the advantages of our STD method and the envelope method. We have described MSTD in the original version of Discussion, and we now elaborate the discussion in light of aforementioned work.

    \begin{quote}
    ``(our method)...can be extended by introducing a more general mixed-effect tensor model. For example, in the special case of Gaussian model, we can model the first two moments of data tensor using
\begin{align}\label{eq:extention}
\mathbb{E}(\tY|\mX_1,\ldots,\mX_K)&=\tC\times\mM_1\times \cdots \times \mM_K,\\
 \text{Var}(\tY|\mX_1,\ldots,\mX_K)&=\mPhi_1\otimes \cdots \otimes \mPhi_K,
\end{align}
where $\mPhi_k\in\mathbb{R}^{d_k\times d_k}$ is the unknown covariance matrix on the mode $k\in[K]$. For general exponential family, an additional mean-variance relationship should also be considered. The joint estimation of mean model $\Theta$ and variance model $\mPhi_k$ will lead to more efficient estimation in the presence of unmeasured confounding effects....Suitable regularization such as .... specially-structured covariance~\citep{li2017parsimonious,lock2018supervised} should be considered...''
    \end{quote}
\end{enumerate}

     \item \textit{Identifiability. Is the proposed model (3) identifiable? It seems not from Definition 1 (Equivalence class). If it’s not identifiable, what benefit does the orthogonality constraint on $\mM_k$ induce? How to interpret the estimated parameters? }

     \textbf{Response:} Our method is to estimate the low-rank tensor $\tB$, or equivalently, the core tensor $\tC$ and factors $\mM_k$ that forms $\tB = \tC \times \{ \mM_1,...,\mM_K \}$. The tensor $\tB$ is identifiable while the factors $\{\tC, \mM_1,...,\mM_K \}$ are not. The non-unique factors incur no concern to the interpretation, because all our parameter estimation and interpretation are about $\tB$.

     The orthonormality of $\mM_k$ is imposed purely for technical convenience. This normalization incurs no impacts in our statistical inference, but may help with numerical stability in empirical optimization~\citep{de2000multilinear, kolda2009tensor}.

    We have added the following discussions in Section~\ref{sec:mainmodel} and Section~\ref{sec:global}:   
     \begin{quote}
         ``...We make several remarks about model identifiability. First, the identifiability of $\tB$ requires the feature matrices $\mX_k$ are of full column rank....Second, the decomposition $\tB = \tC\times\{\mM_1,\ldots,\mM_K\}$ are non-unique, as in standard tensor decomposition~\citep{kolda2009tensor}. For any invertible matrices $\mO_k\in\mathbb{R}^{r_k\times r_k}$, $\tB=\tC\times\{\mM_1,\ldots,\mM_K\}=\tC'\times\{\mM_1\mO_1,\ldots,\mM_K\mO_K\}$ are two equivalent parameterizations with $\tC'=\tC\times\{\mO^{-1}_1,\ldots,\mO^{-1}_K\}$ . To resolve this ambiguity, we impose orthonormality to $\mM_k\in\mathbb{O}(p_k,r_k)$ and assess the estimation error of $\mM_k$ using angle distance. The angle distance is invariant to orthogonal rotations due to its geometric definition. See Section~\ref{subsec:statprob} for more details. The orthonormality of $\mM_k$ is imposed purely for technical convenience. This normalization incurs no impacts in our statistical inference, but may help with numerical stability in empirical optimization~\citep{de2000multilinear, kolda2009tensor}.''
     \end{quote}

   \begin{quote}
       ``...Recall that the factor matrices $\mM_k$ are identifiable only up to orthogonal rotations. Therefore, we choose to use angle distance to assess the estimation accuracy of $\mM_k$...''
   \end{quote}
